Papers

### 2024-10-07 quarto/index.qmd
update

Current research interests: pre-training architectures & scaling, long context (Llama 4).

@@

* Join us for a 2025 research internship! Just email me if you are interested in improving Llama with our team.
* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

>>>>

Current research: pre-training architectures & scaling, long context (Llama 4).

@@

* Join our Llama team for a 2025 research internship! Just email me if you are interested. <a href="https://x.com/astonzhangAZ/status/1843327816055795745" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
